---
title: "Review Paper Eco-innovation: version 04-02-2022"
executivesummary: |
   This is the website of the supplementary material of the review paper.
output:
  html_document:
    theme: flatly
    toc: TRUE
    toc_depth: 2
    number_sections: true
    css: styles.css
    includes:
      after_body: footer.html
---

```{r, echo=F, warning=F, message=F, eval=T, results='hide'}
suppressMessages(library(tidyverse))
suppressMessages(library(dplyr))
suppressMessages(library(kableExtra))
options(knitr.kable.NA = '')

folder <- "C:/Users/User/OneDrive - PUJ Cali/PhD/6. P4_Eco-innov_review/2. Data_review"

# Load results
load(paste(folder, "/3_Co-citation_fa-analysis/Results_FA_eco-innov_201221.rda", sep=""))
```

# Co-citation and Factor Analysis

## Selecting the Core Documents and Identifying the Number of Factors

Three squared matrices with the **60**, **70**, **80**, and **100** most cited documents in the eco-inovation field were used to perform factor analysis. As the number of core documents is unknown a priori, iteration with the three matrices allows to create thresholds to examine the best set of documents that explain the database.

The four matrices with co-citation frequency was converted to a Pearson's correlation matrix using pairwise deletion for managing missing values in the main diagonal.

## Factor Extraction and Selection {.tabset .tabset-fade .tabset-pills}

According to the the Eigenvalue criteria, six factors were extracted for the matrices with **60**, **70** and **80** while the matrix with **100** documents reported seven factors. We report in the below tabs the information of the factors, eigenvalues, proportion variance, and cumulative variance before and after axes oblique rotation.

### 60 references {.unnumbered}
```{r, echo=F, warning=F, message=F, eval=T}
fn32 <- as.data.frame(fn31$Vaccounted) %>% 
  tibble::rownames_to_column("name") %>% 
  gather(var, val, 2:7) %>% 
  tidyr::spread(name, val) %>% 
  select("var", "SS loadings", 
         "Proportion Var", "Cumulative Var") %>% 
  rename("eigenvalue"="SS loadings", 
         "Prop_var"="Proportion Var", 
         "Cum_var"="Cumulative Var") %>%
  arrange(desc(eigenvalue)) %>% 
  mutate(var = 1:n())


f32 <- as.data.frame(f31$Vaccounted) %>% 
  tibble::rownames_to_column("name") %>% 
  gather(var, val, 2:7) %>% 
  tidyr::spread(name, val) %>% 
  select("var", "SS loadings", 
         "Proportion Var", "Cumulative Var") %>% 
  rename("eigenvalue"="SS loadings", 
         "Prop_var"="Proportion Var", 
         "Cum_var"="Cumulative Var") %>% 
  arrange(desc(eigenvalue))  %>% 
  mutate(var = 1:n())

ft32 <- left_join(fn32, f32, by="var") %>%
  mutate(across(where(is.numeric), round, 3))

ft32 %>% 
  kable(caption = "Eigenvalues before and after axes oblique rotation",
        col.names = c("Factor",
                "Eigenvalues","Proportion Var","Cumulative Var",
                "Eigenvalues","Proportion Var","Cumulative Var")) %>% 
  kable_styling(bootstrap_options=c("striped", "condensed", "hover", "responsive"), full_width=F, position="left") %>%
  collapse_rows(valign = "top") %>%  
  add_header_above(c(" " = 1, 
                     "Initial Unrotated FA" = 3, 
                     "Rotated FA" = 3))
```

### 70 references {.unnumbered}
```{r, echo=F, warning=F, message=F, eval=T}
fn42 <- as.data.frame(fn41$Vaccounted) %>% 
  tibble::rownames_to_column("name") %>% 
  gather(var, val, 2:7) %>% 
  tidyr::spread(name, val) %>% 
  select("var", "SS loadings", 
         "Proportion Var", "Cumulative Var") %>% 
  rename("eigenvalue"="SS loadings", 
         "Prop_var"="Proportion Var", 
         "Cum_var"="Cumulative Var") %>% 
  arrange(desc(eigenvalue))  %>% 
  mutate(var = 1:n())

f42 <- as.data.frame(f41$Vaccounted) %>% 
  tibble::rownames_to_column("name") %>% 
  gather(var, val, 2:7) %>% 
  tidyr::spread(name, val) %>% 
  select("var", "SS loadings", 
         "Proportion Var", "Cumulative Var") %>% 
  rename("eigenvalue"="SS loadings", 
         "Prop_var"="Proportion Var", 
         "Cum_var"="Cumulative Var") %>% 
  arrange(desc(eigenvalue))  %>% 
  mutate(var = 1:n())

ft42 <- left_join(fn42, f42, by="var") %>%
  mutate(across(where(is.numeric), round, 3))

ft42 %>% 
  kable(caption = "Eigenvalues before and after axes oblique rotation",
        col.names = c("Factor",
                "Eigenvalues","Proportion Var","Cumulative Var",
                "Eigenvalues","Proportion Var","Cumulative Var")) %>% 
  kable_styling(bootstrap_options=c("striped", "condensed", "hover", "responsive"), full_width=F, position="left") %>%
  collapse_rows(valign = "top") %>%  
  add_header_above(c(" " = 1, 
                     "Initial Unrotated FA" = 3, 
                     "Rotated FA" = 3))
```

### 80 references {.unnumbered}
```{r, echo=F, warning=F, message=F, eval=T}
fn52 <- as.data.frame(fn51$Vaccounted) %>% 
  tibble::rownames_to_column("name") %>% 
  gather(var, val, 2:7) %>% 
  tidyr::spread(name, val) %>% 
  select("var", "SS loadings", 
         "Proportion Var", "Cumulative Var") %>% 
  rename("eigenvalue"="SS loadings", 
         "Prop_var"="Proportion Var", 
         "Cum_var"="Cumulative Var") %>% 
  arrange(desc(eigenvalue))  %>% 
  mutate(var = 1:n())

f52 <- as.data.frame(f51$Vaccounted) %>% 
  tibble::rownames_to_column("name") %>% 
  gather(var, val, 2:7) %>% 
  tidyr::spread(name, val) %>% 
  select("var", "SS loadings", 
         "Proportion Var", "Cumulative Var") %>% 
  rename("eigenvalue"="SS loadings", 
         "Prop_var"="Proportion Var", 
         "Cum_var"="Cumulative Var") %>% 
  arrange(desc(eigenvalue))  %>% 
  mutate(var = 1:n())

ft52 <- left_join(fn52, f52, by="var") %>%
  mutate(across(where(is.numeric), round, 3))

ft52 %>% 
  kable(caption = "Eigenvalues before and after axes oblique rotation",
        col.names = c("Factor",
                "Eigenvalues","Proportion Var","Cumulative Var",
                "Eigenvalues","Proportion Var","Cumulative Var")) %>%
  kable_styling(bootstrap_options=c("striped", "condensed", "hover", "responsive"), full_width=F, position="left") %>%
  collapse_rows(valign = "top") %>%
  add_header_above(c(" " = 1,
                     "Initial Unrotated FA" = 3,
                     "Rotated FA" = 3))
```

### 100 references {.unnumbered}
```{r, echo=F, warning=F, message=F, eval=T}
fn62 <- as.data.frame(fn61$Vaccounted) %>% 
  tibble::rownames_to_column("name") %>% 
  gather(var, val, 2:9) %>% 
  tidyr::spread(name, val) %>% 
  select("var", "SS loadings", 
         "Proportion Var", "Cumulative Var") %>% 
  rename("eigenvalue"="SS loadings", 
         "Prop_var"="Proportion Var", 
         "Cum_var"="Cumulative Var") %>% 
  arrange(desc(eigenvalue))  %>% 
  mutate(var = 1:n())

f62 <- as.data.frame(f61$Vaccounted) %>% 
  tibble::rownames_to_column("name") %>% 
  gather(var, val, 2:8) %>% 
  tidyr::spread(name, val) %>% 
  select("var", "SS loadings", 
         "Proportion Var", "Cumulative Var") %>% 
  rename("eigenvalue"="SS loadings", 
         "Prop_var"="Proportion Var", 
         "Cum_var"="Cumulative Var") %>% 
  arrange(desc(eigenvalue))  %>% 
  mutate(var = 1:n())

ft62 <- left_join(fn62, f62, by="var") %>%
  mutate(across(where(is.numeric), round, 3))

ft62 %>% 
  kable(caption = "Eigenvalues before and after axes oblique rotation",
        col.names = c("Factor",
                "Eigenvalues","Proportion Var","Cumulative Var",
                "Eigenvalues","Proportion Var","Cumulative Var")) %>%
  kable_styling(bootstrap_options=c("striped", "condensed", "hover", "responsive"), full_width=F, position="left") %>%
  collapse_rows(valign = "top") %>%
  add_header_above(c(" " = 1,
                     "Initial Unrotated FA" = 3,
                     "Rotated FA" = 3))
```

## Documents loadings by factor {.tabset .tabset-fade .tabset-pills}

According to the documents' loadings, the six-factor solution with 70 core documents is the most appropriate to explain the underlying structure of eco-innovation studies.

### 60 references {.unnumbered}
```{r, echo=F, warning=F, message=F, eval=T}
f32 <- as.data.frame(unclass(f31$loadings))
f32 <- f32 %>% 
  mutate(across(where(is.numeric), round, 3)) %>% 
  rownames_to_column(var = "ref")
f32[f32 > -0.3 & f32 < 0.3] <- NA
f32 <- arrange(f32, desc(ML2), desc(ML1), desc(ML3),
               desc(ML6), desc(ML4), desc(ML5))

f32 %>% 
  mutate(across(where(is.numeric), round, 3)) %>% 
  kable(col.names = c("Documents",
                "1","2","3","4","5","6")) %>%
  kable_styling(bootstrap_options=c("striped", "condensed", "hover"), full_width=F, position="left") %>% collapse_rows(columns = 1, valign = "top") %>% 
  add_header_above(c(" " = 1, 
                     "Factors" = 6)) %>% 
  scroll_box(width = "75%", height = "500px")
```

### 70 references {.unnumbered}
```{r, echo=F, warning=F, message=F, eval=T}
f42 <- as.data.frame(unclass(f41$loadings))
f42 <- f42 %>% 
  mutate(across(where(is.numeric), round, 3)) %>% 
  rownames_to_column(var = "ref")
f42[f42 > -0.3 & f42 < 0.3] <- NA
f42 <- arrange(f42, desc(ML2), desc(ML1), desc(ML3),
               desc(ML6), desc(ML5), desc(ML4))

f42 %>% 
  mutate(across(where(is.numeric), round, 3)) %>% 
  kable(col.names = c("Documents",
                "1","2","3", "4","5","6")) %>%
  kable_styling(bootstrap_options=c("striped", "condensed", "hover"), full_width=F, position="left") %>% collapse_rows(columns = 1, valign = "top") %>% 
  add_header_above(c(" " = 1, 
                     "Factors" = 6)) %>% 
  scroll_box(width = "75%", height = "500px")
```

### 80 references {.unnumbered}
```{r, echo=F, warning=F, message=F, eval=T}
f52 <- as.data.frame(unclass(f51$loadings))
f52 <- f52 %>% 
  mutate(across(where(is.numeric), round, 3)) %>% 
  rownames_to_column(var = "ref")
f52[f52 > -0.3 & f52 < 0.3] <- NA
f52 <- arrange(f52, desc(ML2), desc(ML3), desc(ML1), desc(ML4),
               desc(ML6), desc(ML5))

f52 %>% 
  mutate(across(where(is.numeric), round, 3)) %>% 
  kable(col.names = c("Documents",
                "1","2","3", "4","5","6")) %>%
  kable_styling(bootstrap_options=c("striped", "condensed", "hover"), full_width=F, position="left") %>% collapse_rows(columns = 1, valign = "top") %>% 
  add_header_above(c(" " = 1, "Factors" = 6)) %>% 
  scroll_box(width = "75%", height = "500px")
```

### 100 references {.unnumbered}
```{r, echo=F, warning=F, message=F, eval=T}
f62 <- as.data.frame(unclass(f61$loadings))
f62 <- f62 %>% 
  mutate(across(where(is.numeric), round, 3)) %>% 
  rownames_to_column(var = "ref")
f62[f62 > -0.3 & f62 < 0.3] <- NA
f62 <- arrange(f62, desc(ML2), desc(ML3), desc(ML4), desc(ML1),
               desc(ML7), desc(ML5), desc(ML6))

f62 %>% 
  mutate(across(where(is.numeric), round, 3)) %>% 
  kable(col.names = c("Documents",
                "1","2","3", "4","5","6", "7")) %>%
  kable_styling(bootstrap_options=c("striped", "condensed", "hover"), full_width=F, position="left") %>% collapse_rows(columns = 1, valign = "top") %>% 
  add_header_above(c(" " = 1, "Factors" = 7)) %>% 
  scroll_box(width = "75%", height = "500px")
```

# Topic Modelling

## Interactive Topic Model Visualization

The 21 topics were clustered in four groups.

```{r, echo=F, warning=F, message=F, eval=T, results='hide'}
folder <- "C:/Users/User/OneDrive - PUJ Cali/PhD/6. P4_Eco-innov_review/2. Data_review"
# Load results
load(paste(folder, "/5_Topic_model_eco-innov/results_LDA_eco-innov_010322.rda", sep=""))
```

```{r, echo=F, warning=F, message=F, eval=T}
library(igraph)
library(visNetwork)

# Definir un umbral
threshold <- 0.091

# Matriz de correlación de valores theta
cormat <- cor(h3$theta)
# summary(cormat)
# matriz de valores absolutos (abs) mayores al umbral
adjmat <- ifelse(abs(cormat) > threshold, 1, 0)
links2 <- as.matrix(adjmat)

# Crea una lista de igraph de una matriz adjacency
net2 <- igraph::graph_from_adjacency_matrix(links2, 
                                            mode = "undirected")

# Crea gráficos que no contienen loops y lineas (edge) múltiples
net2 <- igraph::simplify(net2, 
                         remove.multiple = FALSE, 
                         remove.loops = TRUE)

# Render a visNetwork object from an igraph object
data <- visNetwork::toVisNetworkData(net2)

## Crea la información de los nodos y las líneas
# Aquí se puede dar nombre a los nodos
nodes0 <- data[[1]]
edges <- data[[2]]
```

```{r, echo=F, warning=F, message=F, eval=T}
# Community Detection
# linear time algorithm for detecting community structure in networks
# clp <- igraph::cluster_label_prop(net2)
# clp <- igraph::cluster_louvain(net2, weights = NULL)
clp <- igraph::cluster_edge_betweenness(net2, weights = NULL,
                         directed = F,
                         edge.betweenness = T,
                         merges = TRUE,
                         bridges = TRUE,
                         modularity = TRUE,
                         membership = TRUE
)
nodes0$community <- clp$membership
nodes0$community
## Definir colores para cluster y nodos
# Método 2: aleatoriamente
# qual_col_pals = RColorBrewer::brewer.pal.info[RColorBrewer::brewer.pal.info$category ==
#     "qual", ]
# col_vector = unlist(mapply(RColorBrewer::brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
# col_vector <- c(col_vector, col_vector)
# 
# col <- col_vector[nodes0$community + 1]

# 
links <- igraph::as_data_frame(net2, 
                               what = "edges")
nodes <- igraph::as_data_frame(net2, 
                               what = "vertices")
```

```{r, echo=F, warning=F, message=F, eval=T}
# Help
# visDocumentation()

# save the topic proportions
TopicProportions = colMeans(h3$theta)

# visNetwork preferences
nodes$shape <- "dot"
nodes$shadow <- TRUE  # Nodes will drop shadow
nodes$title <- paste0("Topic ", 1:21)  # Text on click
nodes$size <- (TopicProportions/max(TopicProportions)) * 40  # Node size
nodes$borderWidth <- 0  # Node border width
nodes$group <- nodes0$community
nodes$label <- c("green innov at\nregional scale",
                 "firms' capabilities",
                 "porter hypothesis",
                 "environmental footprint",
                 "small-medium\norganizations",
                 "corporate social\nresponsibility",
                 "supply-chain\nmanagement",
                 "regulatory push-pull",
                 "resource efficiency",
                 "profiting",
                 "circular eco-innovation",
                 "process eco-innovation",
                 "intermediary\norganizations",
                 "cleaner goods",
                 "customers",
                 "networking",
                 "cleaner energy",
                 "competitive advantage",
                 "sustainable and\nsustainability",
                 "eco-innovation for\ndevelopment",
                 "attitudes and behaviors")  # Node label

# nodes$color.background <- col
nodes$color.border <- "gray20"
nodes$color.highlight.background <- "orange"
nodes$color.highlight.border <- "darkred"
nodes$id <- 1:nrow(nodes)

visNetwork(nodes, 
           links,
           width = "100%",
           height = "600px",
           main = "Topic Correlations") %>% 
  visGroups(groupname = "1", color = "#8c510a") %>% 
  visGroups(groupname = "2", color = "#d8b365") %>% 
  visGroups(groupname = "3", color = "#f6e8c3") %>% 
  visGroups(groupname = "4", color = "#5ab4ac") %>% 
  #visGroups(groupname = "5", color = "#01665e") %>% 
  visNodes(font = list(size = 20)) %>% 
  visOptions(highlightNearest = T,
             nodesIdSelection = T) %>% 
  visLayout(randomSeed = 33)
```

## High Probabilities and FREX Words Related to Each Topic

The LDA model was implemented with 19 topics and then grouped based on a similarity score. The following table shows the labels assigned to the clusters and to the topics that compose each cluster. The labels were assigned using the words with the highest probability (column 3) within each topic and the words with the highest frequency-exclusivity score (FREX) (column 4).

 * Highest Prob: are the words within each topic with the highest probability (inferred directly from topic-word distribution parameter β).
 * FREX: are the words that are both frequent and exclusive, identifying words that distinguish topics.

```{r, echo=F, warning=F, message=F, eval=T}
folder <- "C:/Users/User/OneDrive - PUJ Cali/PhD/6. P4_Eco-innov_review/2. Data_review"

cw <- rio::import(paste(folder, "/5_Topic_model_eco-innov/cluster-words_prob-frex.xlsx", sep=""))

cw %>% 
  kable(col.names = c("Cluster",
                      "Cluster label",
                      "Topic",
                      "Topic label",
                      "Probability",
                      "FREX")) %>%
  kable_styling(bootstrap_options=c("striped", "condensed", "hover"), 
                full_width=F, position="left") %>% 
  collapse_rows(columns = 1:2, valign = "top")
```

